% LaTeX file for resume 
% This file uses the resume document class (res.cls)
\documentclass[margin]{res} 
% the margin option causes section titles to appear to the left of body text 
\textwidth=5.2in % increase textwidth to get smaller right margin
\usepackage[T1]{fontenc}
%\usepackage{helvet}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
\usepackage{newcent}   % uses new century schoolbook postscript font 
\usepackage{hyperref}
\hypersetup{
    bookmarks=true,         % show bookmarks bar?
    pdffitwindow=false,     % window fit to page when opened
    pdfstartview={FitH},    % fits the width of the page to the window
    pdftitle={Resume},    % title
    pdfauthor={Author},     % author
    pdfsubject={Resume},   % subject of the document
    pdfcreator={Vikash Pandey},   % creator of the document
    pdfproducer={Producer}, % producer of the document
  %  pdfkeywords={keyword1, key2, key3}, % list of keywords
    pdfnewwindow=true,      % links in new PDF window
    colorlinks=true,       % false: boxed links; true: colored links
    linkcolor=cyan,          % color of internal links (change box color with linkbordercolor)
    citecolor=blue,        % color of links to bibliography
    filecolor=magenta,      % color of file links
    urlcolor=cyan           % color of external links
}


\begin{document} 
 
\name{\textsc{Vikash Pandey}\\[12pt]} % the \\[12pt] adds a blank line after name
 
\address{{Research Scholar} \\ Tata Institute of Fundamental Research \\ Gopanpally \\ Hyderabad, India 500107  \\
        Ph: +91-9581147082\\
        \href{vikashp@tifrh.res.in}{vikashp@tifrh.res.in},
        \href{vikashpandey.phy@gmail.com}{vikashpandey.phy@gmail.com}}

\address{}

 
\begin{resume} 
    \section{Research  \\Interests}
    \begin{itemize}
            \item Particle laden turbulent flow.
            \item Buoyancy-driven bubbly flows. 
            \item Fluid mechanics and turbulence. 
    \end{itemize}

\section{Education} 
    \begin{itemize}
        \item {\bf MSc and PhD in physics} Tata Institute of Fundamental Research,\\ Hyderabad, India. \hfill 2014-21 \\
{\bf Title:} Numerical studies on inertial particles in turbulence and buoyancy-driven bubbly flows.\\
    {\bf Thesis advisor:} Dr. Prasad Perlekar (TIFR-H).\\
    \item {\bf B.Sc. (Physics)} Sikkim Government College, Tadong, India. \hfill 2010 - 13
    \end{itemize} 
    \section{Publications}
\begin{enumerate}
    \item \underline{Vikash Pandey},
        Prasad Perlekar, and Dhrubaditya Mitra, ``Clustering and energy spectra in
        two-dimensional dusty gas turbulence", In:
        \href{https://doi.org/10.1103/PhysRevE.100.013114}{Phys. Rev. E, \textbf{100}, 013114,
        2019}. Selected as Editor's suggestion.
    \item \underline{Vikash Pandey}, Rashmi Ramadugu, and Prasad Perlekar, 
        ``Liquid velocity fluctuations and energy spectra in three-dimensional buoyancy-driven
        bubbly flows", In: \href{https://doi.org/10.1017/jfm.2019.991}{J. Fluid Mech.,
        \textbf{884}, R6, 2019}.
    \item Rashmi  Ramadugu, \underline{Vikash  Pandey}, and Prasad  Perlekar
        ``Pseudo-turbulence in two-dimensional buoyancy-driven bubbly flows: A DNS study'', In: \href{
        DOI: 10.1140/epje/i2020-11997-0} {Eur. Phys. J. E 43 ({\bf 11}) 73 (2020)}.
\item Jan Meibohm, \underline{Vikash Pandey},  Akshay Bhatnagar, Kristian Gustavsson, 
        Dhrubaditya Mitra,  Prasad Perlekar, and B. Mehlig, ``Paths to caustic formation in
        turbulent aerosols", In:
        \href{https://arxiv.org/abs/2012.08424}{arXiv:2012.08424}, 2020
    \item \underline{Vikash Pandey}, Dhrubaditya Mitra, and Prasad Perlekar, ``Turbulence modulation by
        large weakly buoyant bubbles", In: {\it manuscript under
        preparation}.
\end{enumerate}


\section{Experience}
    \begin{itemize}
\item  {\bf Teaching Assistant} Mathematical Methods, TIFR-Hyderabad,\\
    Course advisor: Prof. P. K. Madhu \hfill  2016-17\\
\item  {\bf Teaching Assistant} Classical Mechanics, TIFR-Hyderabad, \\
    Course advisor: Dr. Prasad Perlekar \hfill  2019-20
    \end{itemize}

    \section{Computer \\ Skills}
    \begin{itemize}
        \item {\bf Programming:} FORTRAN, C, CUDA, MPI Parallel Computing,  Python, Matlab
        \item {\bf Softwares:} Visit, Paraview, Mathematica.
    \end{itemize}
    \section{Conferences \\Presentations\\and\\ Workshops}
    \begin{enumerate}
        \item {\it Talk} - American Physical Society, 75$^{th}$ Annual Meeting - DFD, Chicago, \\ USA.\hfill 2020
        \item {\it Workshop} - GPU Application Hackathon, Indian Institute of Science \\ Education and Research, Pune. \hfill  2019.

        \item {\it Poster} - Indian Statistical Physics Community Meeting, International \\ Centre for Theoretical Sciences, Bangalore. \hfill 2019

        \item {\it Poster} - Turbulence from Angstroms to light years, discussion \\ meeting on turbulence, International Centre for Theoretical \\ Sciences, Bangalore. \hfill 2018

        \item {\it Poster} - International Conference on Complex Fluids and Soft Matter \\ (COMPFLU), TIFR-Hyderabad. \hfill 2016
    \end{enumerate} 

\section{References} 
\begin{enumerate}
    \item {\bf Dr. Prasad Perlekar}\\
        Associate Professor, TIFR Centre for Interdisciplinary Sciences,\\ Hyderabad, India 500107. \\
        Email: \href{perlekar@tifrh.res.in}{perlekar@tifrh.res.in}

    \item {\bf Dr. Dhrubaditya Mitra}\\
        Assistant Professor in theoretical physics, NORDITA, Stockholm, \\ Roslagstullsbacken 23 106 91 Stockholm, Sweden. \\
        Email: \href{dhruba.mitra@gmail.com}{dhruba.mitra@gmail.com}
    \item {\bf Dr. Smarajit Karmakar}\\ 
        Associate Professor, TIFR Centre for Interdisciplinary Sciences, \\ Hyderabad, India 500107. \\ 
        Email: \href{smarajit@tifrh.res.in}{smarajit@tifrh.res.in}
\end{enumerate}
   \end{resume} 
\end{document} 



